---
title: "Package Overview: MATH4753bott"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package-overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753bott)
```

# MATH4753bott Package Overview
## Functions
There are a total of 9 functions in this package and they are as follows:

### myfirstfunction
```{r}
myfirstfunction(1:10)
```

### ntickets
```{r}
ntickets(N= 400, p = 0.95, gamma = 0.02)
```

### mysum
```{r}
mysum(1:10)
```

### my_notchplot
```{r}
my_notchplot(fire, DAMAGE)
```

### myncurve
```{r}
myncurve(2, 4, 0.5)
```

### mycltb1
```{r}
mycltb1(n= 10, iter= 10000, p= 0.7)
```

### myboot2
```{r}
sam <- rnorm(25, mean = 6, sd = 0.5)

myboot2(iter= 10000, x= sam, fun= mean, alpha= 0.05)
```

### sample_marbles
```{r}
sample_marbles(iter=4)
```

### birthday
```{r}
birthday(20:24)
```

These functions were used through various labs and assignments.

## Data sets
There is only one data set in this package and that is "fire". "fire" was loaded in as FIREDAM.csv and edited to fit into my package.
```{r}
fire
```

## Challenges
I would like to point out several challenges I had throughout this whole package making process. 

It took me quite a while to figure out why I kept getting an error when I would check this. It was having a problem with this being attached to my OneDrive. I tried several times to get this off and eventually I figured it out.

I think I'm on version two or three of this package because in my process of moving this around so I would stop getting this error, the package would delete itself. GitHub definitely pulled through and was the only thing that saved me from having to do everything all over again.
